\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-12-01 doc/USER_MANUAL/manual_SPECFEM3D.tex
adds paper draft to SPECFEM3D/doc

Seismic networks, such as the Global Seismographic Network (GSN), generally involve various types of instruments with different bandwidths, sampling properties and component configurations. There are standards to name channel codes depending on instrument properties. IRIS  \texttt{(www.iris.edu)} uses SEED format for channel codes, which are represented by three letters, such as \texttt{LHN}, \texttt{BHZ}, etc. In older versions of the SPECFEM3D package, a common format was used for the channel codes of all seismograms, which was \texttt{BHE/BHN/BHZ} for three components. To avoid confusion when comparison are made to observed data, we are now using the IRIS convention for SEM seismograms. In the following, we give a brief explanation of the IRIS convention and how it is adopted in SEM seismograms. Please visit \texttt{www.iris.edu/manuals/SEED\_appA.htm} for further information.\\

\noindent \textbf{\texttt{Band code:}} The first letter in the channel code denotes the band code of seismograms, which depends on the response band and the sampling rate of instruments. The list of band codes used by IRIS is shown in Figure \ref{fig:IRIS_band_codes}. The sampling rate of SEM synthetics is controlled by the resolution of simulations rather than instrument properties. However, for consistency, we follow the IRIS convention for SEM seismograms governed by their sampling rate. For SEM synthetics, we consider band codes for which $dt \leq 1$ s. IRIS also considers the response band of instruments. For instance, short-period and broad-band seismograms with the same sampling rate correspond to different band codes, such as S and B, respectively. In such cases, we consider SEM seismograms as broad band, ignoring the corner period ($\geq 10$ s) of the response band of instruments (note that at these resolutions, the minimum period in the SEM synthetics will be less than $10$ s). Accordingly, when you run a simulation the band code will be chosen depending on the resolution of the synthetics, and channel codes of SEM seismograms will start with either \texttt{L}, \texttt{M}, \texttt{B}, \texttt{H}, \texttt{C} or \texttt{F}, shown by red color in the figure.\\

@@

\caption{The IRIS band code convention is based on the sampling rate and the response band of instruments. Please visit \texttt{www.iris.edu/manuals/SEED\_appA.htm} for further information. Grey rows show the relative band-code range in SPECFEM3D, and the band codes used to name SEM seismograms are denoted in red.}

@@

\noindent \textbf{\texttt{Instrument code:}} The second letter in the channel code corresponds to instrument codes, which specify the family to which the sensor belongs. For instance, \texttt{H} and \texttt{L} are used for high-gain and low-gain seismometers, respectively. The instrument code of SEM seismograms will always be \texttt{X}, as assigned by IRIS for synthetic seismograms. \\

>>>>

Seismic networks, such as the Global Seismographic Network (GSN), generally involve various types of instruments with different bandwidths, sampling properties and component configurations. There are standards to name channel codes depending on instrument properties. IRIS  \texttt{(www.iris.edu)} uses SEED format for channel codes, which are represented by three letters, such as \texttt{LHN}, \texttt{BHZ}, etc. In older versions of the SPECFEM3D package, a common format was used for the channel codes of all seismograms, which was \texttt{BHE/BHN/BHZ} for three components. To avoid confusion when comparison are made to observed data, we are now using the FDSN convention (\url{http://www.fdsn.org/}) for SEM seismograms. In the following, we give a brief explanation of the FDSN convention used by IRIS, and how it is adopted in SEM seismograms. Please visit \texttt{www.iris.edu/manuals/SEED\_appA.htm} for further information.\\

\noindent \textbf{\texttt{Band code:}} The first letter in the channel code denotes the band code of seismograms, which depends on the response band and the sampling rate of instruments. The list of band codes used by IRIS is shown in Figure \ref{fig:IRIS_band_codes}. The sampling rate of SEM synthetics is controlled by the resolution of simulations rather than instrument properties. However, for consistency, we follow the FDSN convention for SEM seismograms governed by their sampling rate. For SEM synthetics, we consider band codes for which $dt \leq 1$ s. IRIS also considers the response band of instruments. For instance, short-period and broad-band seismograms with the same sampling rate correspond to different band codes, such as S and B, respectively. In such cases, we consider SEM seismograms as broad band, ignoring the corner period ($\geq 10$ s) of the response band of instruments (note that at these resolutions, the minimum period in the SEM synthetics will be less than $10$ s). Accordingly, when you run a simulation the band code will be chosen depending on the resolution of the synthetics, and channel codes of SEM seismograms will start with either \texttt{L}, \texttt{M}, \texttt{B}, \texttt{H}, \texttt{C} or \texttt{F}, shown by red color in the figure.\\

@@

\caption{The band code convention is based on the sampling rate and the response band of instruments. Please visit \texttt{www.iris.edu/manuals/SEED\_appA.htm} for further information. Grey rows show the relative band-code range in SPECFEM3D, and the band codes used to name SEM seismograms are denoted in red.}

@@

\noindent \textbf{\texttt{Instrument code:}} The second letter in the channel code corresponds to instrument codes, which specify the family to which the sensor belongs. For instance, \texttt{H} and \texttt{L} are used for high-gain and low-gain seismometers, respectively. The instrument code of SEM seismograms will always be \texttt{X}, as assigned by FDSN for synthetic seismograms. \\
